Scagnostics and Projection Pursuit

### 2018-01-31 Draft/Draft.Rmd
Added guided tour example.

## Test with guided tour
try out scagnostics measures as guided tour index
FIXME still need to write script for this

>>>>

## Test with guided tour
try out scagnostics measures as guided tour index

Example below uses Convex as index function.
We show the evolution of the index on the interpolated guided tour (top) and on the selected planes without interpolation (bottom).
Note that the interpolated projections do not smoothly increase the index value from one selected plane to the next, but shows the unstable nature of the index computation.

```{r guided-tour, include=FALSE}
```
```{r guided-tour-plot, fig.height = 3, fig.cap = "(ref:guided-tour-plot)"}
```

Figure (ref:guided-tour-scatter) compares the scatter plots (left unbinned, right binned) of the start projection, the projection with the lowest index value (t=19 of the interpolated projections) and the final projection (t=28).
```{r guided-tour-scatter, fig.height = 3, fig.cap = "(ref:guided-tour-scatter)"}
```

show computing time? for each index as function of sample size? (long to prepare such a plot..)

### 2018-01-31 Draft/Draft.tex
Added guided tour example.

try out scagnostics measures as guided tour index FIXME still need to
write script for this

>>>>

try out scagnostics measures as guided tour index

Example below uses Convex as index function. We show the evolution of
the index on the interpolated guided tour (top) and on the selected
planes without interpolation (bottom). Note that the interpolated
projections do not smoothly increase the index value from one selected
plane to the next, but shows the unstable nature of the index
computation.

{\centering \includegraphics[width=\textwidth]{figure/guided-tour-plot-1} \includegraphics[width=\textwidth]{figure/guided-tour-plot-2}

\caption[(ref:guided-tour-plot)]{(ref:guided-tour-plot)}\label{fig:guided-tour-plot}
\end{figure}
\end{CodeChunk}

Figure (ref:guided-tour-scatter) compares the scatter plots (left
unbinned, right binned) of the start projection, the projection with the
lowest index value (t=19 of the interpolated projections) and the final
projection (t=28).

{\centering \includegraphics[width=\textwidth]{figure/guided-tour-scatter-1} \includegraphics[width=\textwidth]{figure/guided-tour-scatter-2} \includegraphics[width=\textwidth]{figure/guided-tour-scatter-3}

\caption[(ref:guided-tour-scatter)]{(ref:guided-tour-scatter)}\label{fig:guided-tour-scatter}
\end{figure}
\end{CodeChunk}

show computing time? for each index as function of sample size? (long to
prepare such a plot..)
